raptr: Representative and Adequate Prioritization Toolkit in R

### 2017-08-23 code/rmarkdown/article.Rmd
add gurobi version

To showcase the behavior of the unreliable formulation, we conducted a simulation study and two case studies. To assess how long it would take to solve various sized problems, we also conducted a benchmark analysis (Appendix S2). We completed the analyses using \texttt{R} [version `r getRversion()`; @r192] and solved all optimization problems to within `r general_parameters$MIPGap * 100` % of optimality using \texttt{Gurobi} (version 7.0.2).

@@

# Data accessibility
The \texttt{raptr R} package can be downloaded from The Comprehensive R Archive Network (\url{https://CRAN.R-project.org/package=raptr}). To permit replication and validation of this study, all data, code, and results are stored in an online repository (\url{https://github.com/jeffreyhanson/raptr-manuscript}) and are available at the DOI: \texttt{10.5281/zenodo.846477}.

>>>>

To showcase the behavior of the unreliable formulation, we conducted a simulation study and two case studies. To assess how long it would take to solve various sized problems, we also conducted a benchmark analysis (Appendix S2). We completed the analyses using \texttt{R} [version `r getRversion()`; @r192] and \texttt{raptr} (version 0.0.3). We solved all optimization problems to within `r general_parameters$MIPGap * 100` % of optimality using \texttt{Gurobi} (version 7.0.2).

@@

# Data accessibility
The \texttt{raptr R} package can be downloaded from The Comprehensive R Archive Network (\url{https://CRAN.R-project.org/package=raptr}). To permit replication and validation of this study, all data, code, and results are stored in an online repository (\url{https://github.com/jeffreyhanson/raptr-manuscript}) and are available at the digital object identifier (DOI) \texttt{10.5281/zenodo.847016}.
